External priors for the next generation of CMB experiments.

### 2016-02-09 Notes/response.txt

Thanks, Fixed with Bennett et al. 2003 and Blue book

- ACT and SPT did not follow DASI, they have measured temperature with
ACTPol and SPTPol going for polarization. The first two should go into
the above temperature discussion with references to latest results or
general papers describing the experiments, and the last two should
contribute to the polarization discussion.

We organized the discussion into ground base and satellite experiments. For this reason
we mentioned ACT and SPT toghether with DASI. WE added references to general papers
describing actpol and sptpol.

- In the introduction the cosmological dependence on neutrinos
properties jumps from number to masses to number again, it is
confusing please rephrase.

We introduce the two main topics of that paragraph (N_eff and M_nu) in the first sentence and we then
describe one after the other in the remaining. We strengthen the connector hopefully reducing the confusion.

@@

- Choose between Universe or universe.

Done (Universe)

- Define the cosmological parameters listed in the introduction.

The parameters used in our pipelines are quite standard in the field, and we think that pointing the
reader who wants to know more to the Planck cosmology paper is probably enough.

### 2016-02-09 Notes/response.txt

- The baseline dataset in all the results is using CMB+BAO which means
already CMB + external information. This is confusing, we are not
improving on CMB then but rather on a combination of CMB and some
galaxy data.

The referee is right; we were not clear that CMB+BAO includes current BAO constraints, from e.g., BOSS.
It doesn't make sense to us to exclude things we currently know, so we think it important to include these constraints as our baseline. For example that will strongly bias the foracasted performance of CMB S4 when considered without future BAO experiments like DESI.

- I cannot understand Figures 1,2,3,4. If the far right is the
expected CMB S4+Planck-Pol+BAO15 then the lines starting point should
correspond to prior/sigma = 1. How is it possible than adding a prior
on a parameter 3 times bigger than the sigma from CMB
S4+Planck-Pol+BAO15 (e.g., on Ho) gives a better constrain? If I think
about it in the likelihood space I am multiplying a distribution with
another one having 3 times its width and I do not expect to have any
impact on the combined result. Also, I do not understand why we should
consider adding a prior which is bigger than the baseline sigma from
CMB S4+Planck-Pol+BAO. What is shown on the right axis?

We agree that this was unecessarily complicated so have changed all the figures to absolute priors on the parameters.
We also explicitly describe the right axis that corresponds to the fractional error (obsolute error on the left axis)
The referee's question still remains: why does a 3% prior on H_0 say help if the data itself constrain it to 1%. We stand by our result that it does help. Imagine a 1-D likelihood with one experiment giving a 1% constraint and another [here called "external"] a similar 1% constraint. When combining the 2, the constraint will be tighter, with the new error given by the inverse square root of the sum of the two inverse variances: [1/\sigma_1^2 + 1/\sigma_2^2]^{-1/2}. In the simple example above the external prior is equal to the internal constraint, so the total constraint is reduced by \sqrt{2}. In the example given by the referee [external constraint 3 times looser], there will still be improvement, albeit only by a factor of \sqrt{1 + 1/9}, ~5%. In multi-dimensional space, things are not that simple, but the plots show how things improve. To come back to our first response, we believe this information is extremely important for future planning. While it is true that people have studied degeneracies before, their impact has not been presented in this way. The very fact that the plots are not familiar indicates that we are introducing a new way, a productive way, of thinking about planning. We have added a paragraph in the text that attempts to explain this point more clearly and -- as noted -- have changed the x-axis on all plots to make things less confusing.

### 2016-02-09 Notes/CMBS4_priors_paper.tex
typos fixed

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_scalar_amp(1)_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter $A_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-as}
\end{center}
\end{figure}
%==========

@@

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_omch2_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-omch2}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_scalar_spectral_index(1)_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter $n_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-ns}
\end{center}
\end{figure}
%==========

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_scalar_amp(1)_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $A_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-as}
\end{center}
\end{figure}
%==========

@@

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_omch2_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-omch2}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_re_optical_depth_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the optical depth $\tau$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-tau}
\end{center}
\end{figure}
%==========
